### 2019-04-11 VG500/HW4/submission.tex
add remaining comments, done

\section{Group Exercise}
	I'm the group leader and members are Ning Kang and Reze Rouhi Ardeshiri.

@@

			\item \textbf{Comment by Reze Rouhi Ardeshiri} \newline

@@

			\item \textbf{Comment by Reze Rouhi Ardeshiri} \newline

>>>>

\section{Group Exercise}
	I'm the group leader and members are Ning Kang(017370910016) and Reze Rouhi Ardeshiri(018370990002).

@@

			\item \textbf{Comment by Reze Rouhi Ardeshiri} \newline
				It is clear that Yu has fully studied the section 7 and has an accurate understanding of the content talked in this section. That's why he was able to make a good and understandable summary. It also used good descriptive words to describe the text so that the reader is not tired with reading the text. Although there are weaknesses in grammatically in the text, such as “suggested” instead of “suggest”, “same font like” instead of “same font as”, in general, I can say that it was great. Well done!

@@

			\item \textbf{Comment by Reze Rouhi Ardeshiri} \newline
				Ning had a good summarize for this section. He has played very well with words to describe the text, and this is one of the techniques in writing. I did not see grammatical errors in this text, except for one that in the second paragraph should use “first” instead of “firstly”. In a word, he has done a good job.
